Clean data

### 2018-06-25 01_clean-data.Rmd
Minor changes from upgrading to R 3.5
Better recording of excluded results

# The first 10 rows need to be skipped because the consent question has a bunch
# of line breaks and it messes with CSV line counting. The actual responses
# start on row 11. This doesn't entirely make sense, since read_csv can read the
# line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
results_raw <- read_csv(results_file, skip = 10,
                        col_names = colnames(results_meta))

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- readLines(file.path(here(), "data", "codes_to_exclude.txt")) %>% 
  as.numeric()

# Clean everything
results <- results_raw %>%
  # Only select necessary columns
  select(id = ResponseId, confirmation_code = mTurkCode, duration = `Duration (in seconds)`,
         start_date = StartDate, end_date = EndDate,
         crackdown, issue, funding, starts_with("Q")) %>%
  rename(favor_humanitarian = Q2.1_1, favor_human_rights = Q2.1_2, 
         favor_development = Q2.1_3, donate_likely = Q2.3, 
         amount_donate = Q2.4_1, amount_keep = Q2.4_2, amount_why = Q2.5,
         give_charity = Q3.2, volunteer = Q3.3, political_knowledge = Q3.4,
         ideology = Q3.5, education = Q3.6, religiosity = Q3.7,
         gender = Q3.9, gender_other = Q3.9_4_TEXT, income = Q3.10, age = Q3.11) %>%
  # Clean up experimental condition columns
  mutate(issue = recode(issue, `human rights for refugees` = "Human rights",
                        `humanitarian assistance for refugees` = "Humanitarian assistance"),
         funding = recode(funding, `government donors` = "Government",
                          `individual, private donors` = "Private")) %>%
  mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
                            "Crackdown", "No crackdown")) %>% 
  mutate(crackdown = factor(crackdown, levels = c("No crackdown", "Crackdown"), 
                            ordered = TRUE),
         issue = factor(issue, levels = c("Human rights", "Humanitarian assistance"), 
                        ordered = TRUE),
         funding = factor(funding, levels = c("Government", "Private"), 
                          ordered = TRUE)) %>% 
  # Attention checks
  mutate(attention1_correct = str_split(Q1.3, ",") %>% 
           map_lgl(~ all(attention1_answer %in% .) & length(.) == length(attention1_answer)),
         attention2_correct = Q3.8 == attention2_answer) %>% 
  # This person contacted me separately to say that they accidentally did the first
  # attention check wrong, but that they did pay attention: 6518634
  mutate(attention1_correct = ifelse(confirmation_code == 6518634,
                                     TRUE, attention1_correct)) %>% 
  filter(!(confirmation_code %in% codes_to_exclude)) %>%

@@

saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
```

>>>>

# The first 10 rows need to be skipped because the consent question has a bunch
# of line breaks and it messes with CSV line counting. The actual responses
# start on row 11. This doesn't entirely make sense, since read_csv can read the
# line break-filled row in just fine. Skipping said lines makes it choke. <shrug>
results_raw <- read_csv(results_file, skip = 16,
                        col_names = colnames(results_meta))

# Confirmation codes to exclude. These are people who failed the attention
# checks or who took the survey outside of MTurk.
#
# The code for determining these is in a script that is excluded from the main
# repository because of privacy issues (it deals directly with MTurk worker
# IDs), called "private/approve_mturkers.R". It outputs this text list of codes.
codes_to_exclude <- read_csv(file.path(here(), "data", "codes_to_exclude.csv"))

# Clean everything
results_check_attention <- results_raw %>%
  # Only select necessary columns
  select(id = ResponseId, confirmation_code = mTurkCode, duration = `Duration (in seconds)`,
         start_date = StartDate, end_date = EndDate,
         crackdown, issue, funding, starts_with("Q")) %>%
  rename(favor_humanitarian = Q2.1_1, favor_human_rights = Q2.1_2, 
         favor_development = Q2.1_3, donate_likely = Q2.3, 
         amount_donate = Q2.4_1, amount_keep = Q2.4_2, amount_why = Q2.5,
         give_charity = Q3.2, volunteer = Q3.3, political_knowledge = Q3.4,
         ideology = Q3.5, education = Q3.6, religiosity = Q3.7,
         gender = Q3.9, gender_other = Q3.9_4_TEXT, income = Q3.10, age = Q3.11) %>%
  # Clean up experimental condition columns
  mutate(issue = recode(issue, `human rights for refugees` = "Human rights",
                        `humanitarian assistance for refugees` = "Humanitarian assistance"),
         funding = recode(funding, `government donors` = "Government",
                          `individual, private donors` = "Private")) %>%
  mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
                            "Crackdown", "No crackdown")) %>% 
  mutate(crackdown = factor(crackdown, levels = c("No crackdown", "Crackdown"), 
                            ordered = TRUE),
         issue = factor(issue, levels = c("Human rights", "Humanitarian assistance"), 
                        ordered = TRUE),
         funding = factor(funding, levels = c("Government", "Private"), 
                          ordered = TRUE)) %>% 
  # Attention checks
  mutate(attention1_correct = str_split(Q1.3, ",") %>% 
           map_lgl(~ all(attention1_answer %in% .) & length(.) == length(attention1_answer)),
         attention2_correct = Q3.8 == attention2_answer) %>% 
  # This person contacted me separately to say that they accidentally did the first
  # attention check wrong, but that they did pay attention: 6518634
  mutate(attention1_correct = ifelse(confirmation_code == 6518634,
                                     TRUE, attention1_correct))

results <- results_check_attention %>% 
  filter(!(confirmation_code %in% codes_to_exclude$confirmation_code)) %>%

@@

# Save final clean data
saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
```

```{r completed-summary}
# Save information about completion rates
completed_skeleton <- results_check_attention %>% 
  left_join(codes_to_exclude, by = "confirmation_code") %>% 
  replace_na(list(reason = "Approved")) %>% 
  expand(reason, crackdown, issue, funding)

completed_summary <- results_check_attention %>% 
  left_join(codes_to_exclude, by = "confirmation_code") %>% 
  replace_na(list(reason = "Approved")) %>% 
  count(reason, crackdown, issue, funding) %>% 
  right_join(completed_skeleton, by = c("reason", "crackdown", "issue", "funding")) %>% 
  replace_na(list(n = 0))

saveRDS(completed_summary, file.path(here(), "data", "completion_summary.rds"))
write_csv(completed_summary, file.path(here(), "data", "completion_summary.csv"))
```
